“That’s a BigAss Chicken:  Care and Management of Large Chicken Breeds for Optimal Health and Productivity”

### 2025-03-01 Manuscript_Final.qmd
change name of title

---
title: "That-s-a-BigAss-Chicken"
shorttitle: "Example apaquarto manuscript"
author:
  - name: Karen Veronica Becerra
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Division of the Social Sciences Psychology 
        address: 5801 S Ellis Ave
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
  - name: Kristen M. Johnson
    orcid: 
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Division of the Social Sciences Psychology 
        address: 5801 S Ellis Ave
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637

>>>>

---
title:“That’s a BigAss Chicken:  Care and Management of Large Chicken Breeds for Optimal Health and Productivity”
shorttitle: " "That-s-a-BigAss-Chicken"
author:
  - name: Karen Veronica Becerra
    orcid: 0009-0006-4967-0955
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Division of the Social Sciences Psychology 
        address: 5801 S Ellis Ave
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
  - name: Kristen M. Johnson
    orcid: 
    email: kvbecerra@Uchicago.edu 
    affiliations:
      - name: The University of Chicago 
        department: Division of the Social Sciences Psychology 
        address: 5801 S Ellis Ave
        city: Chicago
        region: IL
        country: USA
        postal-code: 60637
